Identification and performance of stock-recruitment functions in state

### 2024-02-07 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
almost nearly final presentation

# Background

## Introduction

@@

@@

```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'effect_size_glm_glmm_beta_fix.pdf') )
```

@@

 ```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='65%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 're.rec.all.yrs.plot_beta_fix.png') )
  ```

@@

## Assessment error - Spawning Stock Biomass (all years)
- Median unbiased, $\sigma_{R}$ determined quantile range

@@

## Assessment error - Fbar (all years)
- Median unbiased, $\sigma_{R}$ determined quantile range

@@

# Alert
## Is everybody still awake?
 ```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'asleep_keyboard.jpg') )
  ```

@@

- Limiting and Masking had worst performance (BH_3 and BH_4)

@@

## Projections: Specifications and Ecov assumptions 
- Projections were made from the 10th peel of each fitted model (Terminal year - 10)
- A 5-year average of maturity, weight at age, and selectivity specified (time-invariant anyway)
- F in the projection was set at the true OM F value
- The environmental index was treated 3 ways

@@

- In conclusion, we recommend recruitment random effects from a mean SRR as the default EM in WHAM

@@

## Recommendations for further analyses

- In WP-1, we recommended exploring additional levels of $\sigma_{R}$=0.5; however, we note that WP1-Appendix looked at $\sigma_{R}$=0.5 and found no difference

@@

- This work could not have been completed without support from the Microsoft Cooperative Research and Development Agreement (CRADA) and NOAA's National Cloud Program Office (OCIO), as well as MIT (... greg to fill in)
- We thank other members of the SSRTWG for thoughtful comments during earlier discussions and presentations of this work

>>>>

# Intro

## Background

@@

# Sims
## Simulated Data Examples - Type 1
- plots

## Simulated Data Examples - Type 2
- plots

## Simulated Data Examples - Type 3
- plots

@@

```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='60%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'effect_size_glm_glmm_beta_fix.pdf') )
```

@@

 ```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='60%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 're.rec.all.yrs.plot_beta_fix.png') )
  ```

@@

## Assessment error - Spawning Stock Biomass (all years)
- Median unbiased

@@

## Assessment error - Fbar (all years)
- Median unbiased

@@

# !!
## Is everybody still awake?
 ```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'asleep_keyboard.jpg') )
  ```

@@

- Huge quartile ranges; Limiting and Masking had worst performance (BH_3 and BH_4)

@@

## Projections: Specifications and Ecov assumptions 
- Projections were made from the 10th peel of each fitted model (Terminal year - 10)
- A 5-year average of maturity, weight at age, and selectivity specified (time-invariant)
- F in the projection was set at the true OM F value
- The environmental index was treated 3 ways

@@

- In conclusion, we recommend recruitment random effects (ar1) from a mean SRR (recruit_model=2) as the default EM in WHAM

@@

## Further analyses (already investigated, see Appendix for WP-1)

- In WP-1, we recommended exploring additional levels of $\sigma_{R}$=0.5; however, we note that WP1-Appendix looked at $\sigma_{R}$=0.5 and found no difference (only success at unrealistic $\sigma_{R}$=0.1)

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'reg_tree_AIC_best_beta_fix.pdf') )
```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix_384', 'reg_tree_AIC_best_beta_fix_384.pdf') )
```

## Recommendations for future research
- Additional fishing histories, including some that include years with F < $F_{MSY}$
- Recruitment random effect trends
- Ecov models with trends or AR(2) dynamics
- Multivariate ecov processes
- Ecov processes affecting multiple stock parameters, or multiple Ecov processes affecting recruitment (simultaneous or sequential)

@@

- This work could not have been completed without access to high performance computing resources from the Microsoft Cooperative Research and Development Agreement (CRADA) and NOAA's National Cloud Program Office (OCIO), and the MIT Office of Research Computing and Data
- We thank other members of the SSRTWG for thoughtful comments during earlier discussions and presentations of this work
